\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-05-01 project-writings/paper.tex
explain the range propagation algorithm

XXX: rpearl, explain how the analysis pass works; specifically, when
we add things to the worklist, because that is different from the
paper. maybe add pseudocode

>>>>

Our algorithm for range analsis is based on the algorithm due to Gough. It
differs from the paper in a few ways to better fit the architecture of
IonMonkey. The paper suggests using a dominator tree order, but we found that
using reverse post-order was better for our purposes: reverse post-order
traversal is simpler to implement in IonMonkey, and in general definitions are
still visited before all their uses. There is no issue of correctness since we
iterate until no range information is changing..

We compute the range of each definition unconditionally once, and add all phi
nodes and beta nodes to a worklist--the only values which can change are those
that flow through backedges captured by phis. We then iterate through the
worklist, recomputing the range of each definition, and add all consumers of
that definition if the range changed in order to propagate this information.

\begin{lstlisting}[language=Python,
                   caption={Pseudocode algorithm for propagating range information},
                   label={lst:propagate_ranges}]
def propagateRanges(graph):
    worklist = []
    for block in reversePostOrder(graph):
        for insn in block:
            insn.recomputeRange()
            if !insn.isPhi() and !insn.isBeta():
                continue
            worklist.appendAll(insn.uses())

    while len(worklist) > 0:
        insn = worklist.pop()
        #recomputeRange() returns true if the range changed
        if (insn.recomputeRange()):
            worklist.appendAll(insn.uses())
\end{lstlisting}
